---
title: "Chapter1_figures"
author: "Andreas Norlin"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

rm(list = ls())

package.list <- c("dplyr","tidyverse","ggplot2",
                  "lemon","vegan","Rmisc",
                  "lubridate","patchwork","stringi",
                  "RColorBrewer","pheatmap","ggh4x")

if(!all(package.list %in% installed.packages()[,"Package"])){
  install.packages(package.list[!(package.list %in% installed.packages()[,"Package"])])
}

bioc.packages <- c("phyloseq","DESeq2","rain","limma","clusterProfiler")

if(!all(bioc.packages %in% installed.packages()[,"Package"])){
  if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install(bioc.packages[!(bioc.packages %in% installed.packages()[,"Package"])])
}

library(dplyr)
library(tidyverse)
library(ggplot2)
library(lemon)
library(vegan)
library(Rmisc)
library(lubridate)
library(RColorBrewer)
library(pheatmap)
library(ggh4x)

library(phyloseq)
library(patchwork)
library(DESeq2)
library(stringi)

library(rain)
library(limma)
library(clusterProfiler)

colors=c('#e9e9e9','#C14450','#f0b08f','#c2aba6','#60555f','#3c6481','#9fd6e6','#256F64','#63a375')

red<- c("#EB8B8E","#FBD5E2","#E7B6AF","#AC6873", "#D82354","darkred")
orange <- c("#FAAA6D","#FECF92")
yellow <- c("#FFC317","#F7F4B7", "#CC9C3C")
green <- c("#16866F","#1E3F1C","#99A339","#516A65","#8BC89F","darkgreen")
blue <- c("#005694","#B7E1DD","#66879E","#1BAAE2","#5FC8D8","darkblue")
purple <- c("#E7D7CE","#A699A9","#434582","#81347D", "#B5218E")

Euk.color <- c("#8BC89F","#5FC8D8",'#C14450')
Bact.color <- c("#F7F4B7", "#CC9C3C")

colors30 <- c(blue, purple, red, yellow, orange, green, "black")

plot.width <- 10/1.5
plot.height <- 6/1.5

save_plots <- F
```

## Distribution plots:

This section is for creating distribution plots, like bar plots and pie charts

```{r}
# load("CSV_files/Full.merged.RData",verbose = T)
# salmon.numreads <- read.csv("CSV_files/salmon.merged.TPM.subset5.csv")
# 
# names(Full.merged) <- unlist(lapply(names(Full.merged),
#                                     function(x){unlist(strsplit(x,
#                                                                 split = "_",
#                                                                 fixed = TRUE))[1]}))
# 
# filter <- names(Full.merged) %in% names(salmon.numreads)
# 
# Full.merged <- Full.merged[,!filter]
# 
# Full.merged <- merge(salmon.numreads,Full.merged,
#                      by.x = "Name",by.y = "SequenceID",
#                      all.x = TRUE)
# 
# TPM.TaxFunc <- Full.merged
# 
# save(TPM.TaxFunc,meta.data,file = "CSV_files/TPM_TaxFunc.RData")
# 
# rm(list = c("salmon.numreads","filter"))
```

```{r}
load("CSV_files/TPM_TaxFunc.RData",verbose = T)


```

## Taxonomic annotation of contigs:

The following plot shows how many contigs has been annotated to the specific taxonomical level.

```{r}
TaxHierach <- c("Domain","Supergroup","Division","Class","Order","Family","Genus","Species")

# for(i in 1:length(TaxHierach)){
#   if(i == 1){
#     vec <- rep(NA,length(TaxHierach))
#   }
# 
# 
# 
#   vec[i] <- (sum(!is.na(TPM.TaxFunc[,TaxHierach[i]]))/nrow(TPM.TaxFunc))*100
# }

for(i in 1:length(TaxHierach)){
  if(i == 1){
    vec <- rep(NA,length(TaxHierach))
  }
  
  filter <- !is.na(TPM.TaxFunc[,TaxHierach[i]])
  
  vec[i] <- (sum(TPM.TaxFunc[filter,paste(meta.data$SampleID,"quant",sep = "_")])/sum(TPM.TaxFunc[,paste(meta.data$SampleID,"quant",sep = "_")]))*100
}

dfOut <- cbind.data.frame("fill" = TaxHierach,"Annotated" = vec,"Unannotated" = 100-vec) %>% 
  pivot_longer(cols = c(2,3),names_to = "Annot",values_to = "values")

ggplot(dfOut)+
  geom_bar(aes(fill=Annot,
               x = factor(fill,levels = TaxHierach),
               y = values),
           position = "stack",
           stat = "identity")+
  geom_point(data = dfOut[dfOut$Annot == "Annotated",],
             aes(x = fill,
                 y = values*50,
                 color = Annot))+
  scale_y_continuous(breaks = c(0,20,40,60,80,100),
                     sec.axis = sec_axis(~./50, name = "% Annotated"))+
  scale_fill_manual(values = c("Annotated" = "dodgerblue",
                               "Unannotated" = "grey"))+
  scale_color_manual(values = c("Annotated" = "black"))+
  labs(x = "Taxonomic level",
       y = "% of normalized reads",
       title = "Annotated contigs to specific taxonomical level",
       caption = "The dots indicate the percentage of contigs that are\n annotated at that level, plotted on the seconday y-axis",
       fill = "Annotated",
       color = "")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 45,vjust = 0.5))

if(save_plots){
  ggsave("Chapter1_plots/TPM_annotatedTaxBar.png",dpi = 300,height = plot.height,width = plot.width)
}
```
It might not be very apparent, but less than 1.5% of all the reads have been assigned to a Domain, and the sharp decline occurs at class.

## Distributions at taxonomic levels:

```{r}
load("CSV_files/Full.merged.RData",verbose = T)
source("summary_count.R")

# Removing NAs from the Division column, by renaming them as resolved, and whatever their highest resolved taxonomy is.
na.filter <- is.na(Full.merged$Division)
Full.merged$Division[na.filter] <- paste("Unresolved",Full.merged$classification[na.filter],sep = "_")

names(Full.merged) <- unlist(lapply(names(Full.merged),function(x){unlist(strsplit(x,split = "_"))[1]}))

# Setting up the summary count function and running it.
day.vec <- meta.data$SampleID
df.count <- summary_count(Full.merged,Col_vec = day.vec,Col_filter = "Division")

# Finding all the groups that appear in top n at least once.
n.top <- 10

for(i in 1:ncol(df.count)){
  if(i == 1){
    name.vec <- names(df.count)
  }
  
  vec <- row.names(df.count)[order(df.count[,name.vec[i]],decreasing = T)[1:n.top]]
  
  if(i == 1){
    top.Div <- vec
  } else{
    if(all(vec %in% top.Div)){
      
    }else{
     top.Div <- c(top.Div,vec[!(vec %in% top.Div)]) 
    }
  }
}

top_filter <- row.names(df.count) %in% top.Div

df.count <- data.frame(apply(df.count,2,function(x){x/sum(x)}))

df.count$Division <- row.names(df.count)
df.count$Division[!top_filter] <- "other"

meta.data$Replicate <- unlist(lapply(meta.data$SampleName,function(x){substr(x,start = nchar(x),stop = nchar(x))}))

dfOut <- pivot_longer(df.count,cols = all_of(day.vec),names_to = "SampleID",values_to = "TPM")
dfOut <- merge(dfOut,meta.data[,c("SampleID","SampleName","AssemblyGroup","Day.num","ToD","Replicate")],by = "SampleID")

df.TopDiv <- cbind.data.frame("Domain" = Full.merged$Domain[Full.merged$Division %in% top.Div],
                              "Division" = Full.merged$Division[Full.merged$Division %in% top.Div]) %>% 
  distinct(Division, .keep_all = T)

for(i in 1:length(top.Div)){
  if(i == 1){
    vec <- rep(NA,length(top.Div))
    vec.color <- rep(NA,length(top.Div))
    
    n <- 1
    m <- 1
  }
  
  vec[i] <- unique(Full.merged$Domain[Full.merged$Division %in% top.Div[i]])
  
  if(vec[i] =="Bacteria"){
    vec.color[i] <- yellow[n]
    
    n <- n+1
  } else{
    vec.color[i] <- c(blue,green,red)[m]
    m <- m+1
  }
  
  if(i == length(top.Div)){
    div.colors <- c(vec.color,"grey")
    
    names(div.colors) <- c(top.Div,"other")
  }
}



order.vec1 <- c("Day1_afternoon","Day1_evening","Day1_night","Day1_morning",
               "Day2_night","Day2_morning","Day2_afternoon","Day2_evening")

labels.vec1 <- c("Afternoon","Evening","Night","Morning",
                 "Night ","Morning ","Afternoon ","Evening ")

order.vec2 <- c("Day1_morning","Day1_afternoon","Day1_evening","Day1_night",
               "Day2_morning","Day2_afternoon","Day2_evening","Day2_night")

labels.vec2 <- c("Morning","Afternoon","Evening","Night",
                 "Morning ","Afternoon ","Evening ","Night ")

dfOut$AssemblyGroup <- factor(dfOut$AssemblyGroup,
                              levels = order.vec1,
                              labels = labels.vec1)

ggplot(dfOut) +
    geom_bar(aes(fill = factor(Division, levels = c(top.Div, "other")),
                 x = Replicate,
                 y = TPM),
             position = "stack", stat = "identity") +
    facet_nested(~factor(Day.num,levels = c("Day1","Day2"),labels = c("Day 1", "Day 2"))+
                   AssemblyGroup) +
    theme_classic()+
  labs(x = "Sample",
       y = "Fraction of annotated TPM",
       title = "Top Division represented",
       fill = "Division")+
  scale_fill_manual(values = div.colors)+
  theme(axis.text.x = element_blank())+
  guides(fill = guide_legend(ncol=2))

if(save_plots){
  ggsave("Chapter1_plots/TPM_DivisionBars.png",dpi = 300,height = plot.height,width = plot.width*1.5)
}
```

```{r}
load("CSV_files/Full.merged.RData",verbose = T)
source("summary_count.R")

# Removing NAs from the Class column, by renaming them as resolved, and whatever their highest resolved taxonomy is.
na.filter <- is.na(Full.merged$Class)
Full.merged$Class[na.filter] <- paste("Unresolved",Full.merged$classification[na.filter],sep = "_")

names(Full.merged) <- unlist(lapply(names(Full.merged),function(x){unlist(strsplit(x,split = "_"))[1]}))

# Setting up the summary count function and running it.
day.vec <- meta.data$SampleID
df.count <- summary_count(Full.merged,Col_vec = day.vec,Col_filter = "Class")

# Finding all the groups that appear in top n at least once.
n.top <- 10

for(i in 1:ncol(df.count)){
  if(i == 1){
    name.vec <- names(df.count)
  }
  
  vec <- row.names(df.count)[order(df.count[,name.vec[i]],decreasing = T)[1:n.top]]
  
  if(i == 1){
    top.Div <- vec
  } else{
    if(all(vec %in% top.Div)){
      
    }else{
     top.Div <- c(top.Div,vec[!(vec %in% top.Div)]) 
    }
  }
}

top_filter <- row.names(df.count) %in% top.Div

df.count <- data.frame(apply(df.count,2,function(x){x/sum(x)}))

df.count$Class <- row.names(df.count)
df.count$Class[!top_filter] <- "other"

meta.data$Replicate <- unlist(lapply(meta.data$SampleName,function(x){substr(x,start = nchar(x),stop = nchar(x))}))

dfOut <- pivot_longer(df.count,cols = all_of(day.vec),names_to = "SampleID",values_to = "TPM")
dfOut <- merge(dfOut,meta.data[,c("SampleID","SampleName","AssemblyGroup","Day.num","ToD","Replicate")],by = "SampleID")

for(i in 1:length(top.Div)){
  if(i == 1){
    vec <- rep(NA,length(top.Div))
    vec.color <- rep(NA,length(top.Div))
    
    n <- 1
    m <- 1
  }
  
  vec[i] <- unique(Full.merged$Domain[Full.merged$Class %in% top.Div[i]])
  
  if(vec[i] =="Bacteria"){
    vec.color[i] <- yellow[n]
    
    n <- n+1
  } else{
    vec.color[i] <- c(blue,green,red)[m]
    m <- m+1
  }
  
  if(i == length(top.Div)){
    div.colors <- c(vec.color,"grey")
    
    names(div.colors) <- c(top.Div,"other")
  }
}

order.vec1 <- c("Day1_afternoon","Day1_evening","Day1_night","Day1_morning",
               "Day2_night","Day2_morning","Day2_afternoon","Day2_evening")

labels.vec1 <- c("Afternoon","Evening","Night","Morning",
                 "Night ","Morning ","Afternoon ","Evening ")

order.vec2 <- c("Day1_morning","Day1_afternoon","Day1_evening","Day1_night",
               "Day2_morning","Day2_afternoon","Day2_evening","Day2_night")

labels.vec2 <- c("Morning","Afternoon","Evening","Night",
                 "Morning ","Afternoon ","Evening ","Night ")

dfOut$AssemblyGroup <- factor(dfOut$AssemblyGroup,
                              levels = order.vec1,
                              labels = labels.vec1)

ggplot(dfOut) +
    geom_bar(aes(fill = factor(Class, levels = c(top.Div, "other")),
                 x = Replicate,
                 y = TPM),
             position = "stack", stat = "identity") +
    facet_nested(~factor(Day.num,levels = c("Day1","Day2"),labels = c("Day 1", "Day 2"))+
                   AssemblyGroup) +
    theme_classic()+
  labs(x = "Sample",
       y = "Fraction of annotated TPM",
       title = "Top Classes represented",
       fill = "Class")+
  scale_fill_manual(values = div.colors)+
  theme(axis.text.x = element_blank())+
  guides(fill = guide_legend(ncol=2))

if(save_plots){
  ggsave("Chapter1_plots/TPM_ClassBars.png",dpi = 300,height = plot.height,width = plot.width*1.5)
}
```

```{r}
load("CSV_files/Full.merged.RData",verbose = T)
source("summary_count.R")

# Removing NAs from the Genus column, by renaming them as resolved, and whatever their highest resolved taxonomy is.
na.filter <- is.na(Full.merged$Genus)
Full.merged$Genus[na.filter] <- paste("Unresolved",Full.merged$classification[na.filter],sep = " ")

names(Full.merged)[grep("HM",names(Full.merged))] <- unlist(lapply(names(Full.merged)[grep("HM",names(Full.merged))],
                                                                   function(x){unlist(strsplit(x,split = "_"))[1]}))

Full.merged$Genus[Full.merged$Genus == "Uncertain"] <- paste("Uncertain",Full.merged$Family[Full.merged$Genus == "Uncertain"],sep = " ")

# Setting up the summary count function and running it.
day.vec <- meta.data$SampleID
df.count <- summary_count(Full.merged,Col_vec = day.vec,Col_filter = "Genus")

# Finding all the groups that appear in top n at least once.
n.top <- 10

for(i in 1:ncol(df.count)){
  if(i == 1){
    name.vec <- names(df.count)
  }
  
  vec <- row.names(df.count)[order(df.count[,name.vec[i]],decreasing = T)[1:n.top]]
  
  if(i == 1){
    top.Div <- vec
  } else{
    if(all(vec %in% top.Div)){
      
    }else{
     top.Div <- c(top.Div,vec[!(vec %in% top.Div)]) 
    }
  }
}

top_filter <- row.names(df.count) %in% top.Div

df.count <- data.frame(apply(df.count,2,function(x){x/sum(x)}))

df.count$Genus <- row.names(df.count)
df.count$Genus[!top_filter] <- "other"

meta.data$Replicate <- unlist(lapply(meta.data$SampleName,function(x){substr(x,start = nchar(x),stop = nchar(x))}))

dfOut <- pivot_longer(df.count,cols = all_of(day.vec),names_to = "SampleID",values_to = "TPM")
dfOut <- merge(dfOut,meta.data[,c("SampleID","SampleName","AssemblyGroup","Day.num","ToD","Replicate")],by = "SampleID")

for(i in 1:length(top.Div)){
  if(i == 1){
    vec <- rep(NA,length(top.Div))
    vec.color <- rep(NA,length(top.Div))
    
    n <- 1
    m <- 1
  }
  
  vec[i] <- unique(Full.merged$Domain[Full.merged$Genus %in% top.Div[i]])
  
  if(vec[i] =="Bacteria"){
    vec.color[i] <- yellow[n]
    
    n <- n+1
  } else{
    vec.color[i] <- c(blue,green,red)[m]
    m <- m+1
  }
  
  if(i == length(top.Div)){
    div.colors <- c(vec.color,"grey")
    
    names(div.colors) <- c(top.Div,"other")
  }
}

order.vec1 <- c("Day1_afternoon","Day1_evening","Day1_night","Day1_morning",
               "Day2_night","Day2_morning","Day2_afternoon","Day2_evening")

labels.vec1 <- c("Afternoon","Evening","Night","Morning",
                 "Night ","Morning ","Afternoon ","Evening ")

order.vec2 <- c("Day1_morning","Day1_afternoon","Day1_evening","Day1_night",
               "Day2_morning","Day2_afternoon","Day2_evening","Day2_night")

labels.vec2 <- c("Morning","Afternoon","Evening","Night",
                 "Morning ","Afternoon ","Evening ","Night ")

dfOut$AssemblyGroup <- factor(dfOut$AssemblyGroup,
                              levels = order.vec1,
                              labels = labels.vec1)

Uncertain.vec <- top.Div[grep(c("Uncertain"),top.Div)]
Unresolved.vec <- top.Div[grep(c("Unresolved"),top.Div)]
top.Div <- c(top.Div[!(top.Div %in% c(Uncertain.vec,Unresolved.vec))],Uncertain.vec,Unresolved.vec)

ggplot(dfOut) +
    geom_bar(aes(fill = factor(Genus, levels = c(top.Div, "other")),
                 x = Replicate,
                 y = TPM),
             position = "stack", stat = "identity") +
    facet_nested(~factor(Day.num,levels = c("Day1","Day2"),labels = c("Day 1", "Day 2"))+
                   AssemblyGroup) +
    theme_classic()+
  labs(x = "Sample",
       y = "Fraction of annotated TPM",
       title = "Top Genus represented",
       fill = "Genus")+
  scale_fill_manual(values = div.colors)+
  theme(axis.text.x = element_blank())+
  guides(fill = guide_legend(ncol=2))

if(save_plots){
  ggsave("Chapter1_plots/TPM_GenusBars.png",dpi = 300,height = plot.height,width = plot.width*1.5)
}
```


```{r}
load("CSV_files/Full.merged.RData",verbose = T)
source("summary_count.R")

# Removing NAs from the Species column, by renaming them as resolved, and whatever their highest resolved taxonomy is.
na.filter <- is.na(Full.merged$Species)
Full.merged$Species[na.filter] <- paste("Unresolved",Full.merged$classification[na.filter],sep = " ")

names(Full.merged)[grep("HM",names(Full.merged))] <- unlist(lapply(names(Full.merged)[grep("HM",names(Full.merged))],
                                                                   function(x){unlist(strsplit(x,split = "_"))[1]}))

Full.merged$Species[Full.merged$classification == "Uncertain"] <- paste("Uncertain",Full.merged$Genus[Full.merged$classification == "Uncertain"],sep = " ")
Full.merged$Species[Full.merged$Species == "Uncertain Uncertain"] <- paste("Uncertain",Full.merged$Family[Full.merged$Species == "Uncertain Uncertain"],sep = " ")

# Setting up the summary count function and running it.
day.vec <- meta.data$SampleID
df.count <- summary_count(Full.merged,Col_vec = day.vec,Col_filter = "Species")

# Finding all the groups that appear in top n at least once.
n.top <- 10

for(i in 1:ncol(df.count)){
  if(i == 1){
    name.vec <- names(df.count)
  }
  
  vec <- row.names(df.count)[order(df.count[,name.vec[i]],decreasing = T)[1:n.top]]
  
  if(i == 1){
    top.Div <- vec
  } else{
    if(all(vec %in% top.Div)){
      
    }else{
     top.Div <- c(top.Div,vec[!(vec %in% top.Div)]) 
    }
  }
}

top_filter <- row.names(df.count) %in% top.Div

df.count <- data.frame(apply(df.count,2,function(x){x/sum(x)}))

df.count$Species <- row.names(df.count)
df.count$Species[!top_filter] <- "other"

meta.data$Replicate <- unlist(lapply(meta.data$SampleName,function(x){substr(x,start = nchar(x),stop = nchar(x))}))

dfOut <- pivot_longer(df.count,cols = all_of(day.vec),names_to = "SampleID",values_to = "TPM")
dfOut <- merge(dfOut,meta.data[,c("SampleID","SampleName","AssemblyGroup","Day.num","ToD","Replicate")],by = "SampleID")

for(i in 1:length(top.Div)){
  if(i == 1){
    vec <- rep(NA,length(top.Div))
    vec.color <- rep(NA,length(top.Div))
    
    n <- 1
    m <- 1
  }
  
  vec[i] <- unique(Full.merged$Domain[Full.merged$Species %in% top.Div[i]])
  
  if(vec[i] =="Bacteria"){
    vec.color[i] <- yellow[n]
    
    n <- n+1
  } else{
    vec.color[i] <- c(blue,green,red)[m]
    m <- m+1
  }
  
  if(i == length(top.Div)){
    div.colors <- c(vec.color,"grey")
    
    names(div.colors) <- c(top.Div,"other")
  }
}

order.vec1 <- c("Day1_afternoon","Day1_evening","Day1_night","Day1_morning",
               "Day2_night","Day2_morning","Day2_afternoon","Day2_evening")

labels.vec1 <- c("Afternoon","Evening","Night","Morning",
                 "Night ","Morning ","Afternoon ","Evening ")

order.vec2 <- c("Day1_morning","Day1_afternoon","Day1_evening","Day1_night",
               "Day2_morning","Day2_afternoon","Day2_evening","Day2_night")

labels.vec2 <- c("Morning","Afternoon","Evening","Night",
                 "Morning ","Afternoon ","Evening ","Night ")

dfOut$AssemblyGroup <- factor(dfOut$AssemblyGroup,
                              levels = order.vec1,
                              labels = labels.vec1)

Uncertain.vec <- top.Div[grep(c("Uncertain"),top.Div)]
Unresolved.vec <- top.Div[grep(c("Unresolved"),top.Div)]
top.Div <- c(top.Div[!(top.Div %in% c(Uncertain.vec,Unresolved.vec))],Uncertain.vec,Unresolved.vec)

ggplot(dfOut) +
    geom_bar(aes(fill = factor(Species, levels = c(top.Div, "other")),
                 x = Replicate,
                 y = TPM),
             position = "stack", stat = "identity") +
    facet_nested(~factor(Day.num,levels = c("Day1","Day2"),labels = c("Day 1", "Day 2"))+
                   AssemblyGroup) +
    theme_classic()+
  labs(x = "Sample",
       y = "Fraction of annotated TPM",
       title = "Top Species represented",
       fill = "Species")+
  scale_fill_manual(values = div.colors)+
  theme(axis.text.x = element_blank())+
  guides(fill = guide_legend(ncol=2))

if(save_plots){
  ggsave("Chapter1_plots/TPM_SpeciesBars.png",dpi = 300,height = plot.height,width = plot.width*1.5)
}
```

## Time series figures:
First figure here shows the distribution of cycles that was found, including how many at each cycle patter was significant and insignificant.

```{r}
load("CSV_files/FullMerged_rain.RData",verbose = T)

Full.merged_rain$phase.peaks <- paste(Full.merged_rain$phase,Full.merged_rain$peak.shape,sep = "+")
phase.peaks <- factor(unique(Full.merged_rain$phase.peaks),
                      levels = c("Morning+6","Morning+12","Morning+18",
                                 "Afternoon+6","Afternoon+12","Afternoon+18",
                                 "Evening+6","Evening+12","Evening+18",
                                 "Night+6","Night+12","Night+18"))

for(i in 1:length(phase.peaks)){
  if(i == 1){
    vec.sig <- rep(NA,length(phase.peaks))
    vec.insig <- rep(NA,length(phase.peaks))
  }
  
  filter <- Full.merged_rain$phase.peaks == phase.peaks[i]
  
  df.temp <- Full.merged_rain[filter,]
  
  vec.sig[i] <- sum(df.temp$Sig == "Sig")
  vec.insig[i] <- sum(df.temp$Sig == "Insig")
  
  if(i == length(phase.peaks)){
    dfOut <- cbind.data.frame(phase.peaks,"Sig" = vec.sig,"Insig" = vec.insig)
  }
}

rm(list = "Full.merged_rain")

axis2.Scale <- 200000/1e6

ggplot()+
  geom_bar(data = dfOut%>%pivot_longer(cols = 2:3,
                                       names_to = "Sig",
                                       values_to = "Value"),
           aes(x = phase.peaks,
               y = Value/1e6,
               fill = Sig),
           position = "stack",stat = "identity")+
  geom_point(data = dfOut,
             aes(x = phase.peaks,
                 y = (Sig/(Sig+Insig))*axis2.Scale*100))+
  scale_y_continuous(sec.axis = sec_axis(~./axis2.Scale, name = "% Significant"))+
  scale_fill_manual(values = c("Sig" = "dodgerblue",
                               "Insig" = "goldenrod"))+
  labs(x = "Peak phase + hours until valley",
       y = expression("Occurences x 10"^6),
       fill = "Significance")+
  theme_classic()

if(save_plots){
  ggsave("Chapter1_plots/TPM_RainSigBars.png",dpi = 300,height = plot.height,width = plot.width+2)
}

```


```{r}
load("CSV_files/FullMerged_rain.RData",verbose = T)

Full.merged_rain$phase.peaks <- paste(Full.merged_rain$phase,Full.merged_rain$peak.shape,sep = "+")
phase.peaks <- factor(unique(Full.merged_rain$phase.peaks),
                      levels = c("Morning+6","Morning+12","Morning+18",
                                 "Afternoon+6","Afternoon+12","Afternoon+18",
                                 "Evening+6","Evening+12","Evening+18",
                                 "Night+6","Night+12","Night+18"))

COG_categories <- sort(unique(unlist(lapply(unique(Full.merged_rain$COG_category),
                                            function(x){strsplit(x,split = "")}))))

Full.merged_rain$COG_category[is.na(Full.merged_rain$COG_category)] <- "na"

COG_categories <- c(COG_categories,"na")

for(i in 1:length(phase.peaks)){
  if(i == 1){
    df.sig <- data.frame(matrix(NA,nrow = length(phase.peaks),ncol = length(COG_categories)))
    df.insig <- data.frame(matrix(NA,nrow = length(phase.peaks),ncol = length(COG_categories)))
    
    names(df.sig) <- COG_categories
    df.sig$phase.peaks <- phase.peaks
    
    names(df.insig) <- COG_categories
    df.insig$phase.peaks <- phase.peaks
  }
  
  filter <- Full.merged_rain$phase.peaks == phase.peaks[i]
  df.temp <- Full.merged_rain[filter,]
  
  for(j in 1:length(COG_categories)){
    df.sig[i,j] <- length(grep(COG_categories[j],df.temp$COG_category[df.temp$Sig == "Sig"]))
    df.insig[i,j] <- length(grep(COG_categories[j],df.temp$COG_category[df.temp$Sig == "Insig"]))
  }
  
  if(i == length(phase.peaks)){
    df.sig$Total <- apply(df.sig[,COG_categories],1,sum)
    df.insig$Total <- apply(df.insig[,COG_categories],1,sum)
    
    df.sig$Sig <- "Sig"
    df.insig$Sig <- "Insig"
    
    dfOut <- rbind.data.frame(df.sig,df.insig)
    
    rm(list = c("df.sig","df.insig","df.temp"))
  }
}
dfOut$tp <- apply(dfOut[,COG_categories],1,sum)

dfOut2 <- dfOut %>% pivot_longer(cols = all_of(c(COG_categories,"tp")),
                                 names_to = "COG",
                                 values_to = "Count")

ggplot(dfOut2[!(dfOut2$COG %in% c("na","tp")),])+
  geom_bar(aes(fill = Sig,
               x = COG,
               y = Count),
           position = "stack",stat = "identity")+
  facet_wrap(facets = "phase.peaks", nrow = 4,ncol = 3,scales = "free_y")+
  theme_classic()

if(save_plots){
  ggsave("Chapter1_plots/zzCOG_RainSigBars.png",dpi = 300,height = plot.height*4/3,width = plot.width*4/3)
}


dfOut2$TotPhase.COG <- rep(dfOut2$Count[dfOut2$Sig == "Insig"] + dfOut2$Count[dfOut2$Sig == "Sig"],2)


dfOut2 <- dfOut2[dfOut2$Sig == "Sig",]
dfOut2$Sig.rat <- dfOut2$Count/dfOut2$TotPhase.COG
dfOut2$ColorGroup <- NA

for(i in 1:length(phase.peaks)){
  filter <- dfOut2$phase.peaks == phase.peaks[i]
  df.temp <- dfOut2[filter,]
  
  dfOut2$ColorGroup[filter] <- unlist(lapply(df.temp$Sig.rat,function(x){ifelse(x > df.temp$Sig.rat[df.temp$COG == "tp"],
                                                                              "Higher","Lower")}))
  
  if(i == length(phase.peaks)){
    dfOut2$ColorGroup[dfOut2$COG == "na"] <- "unannotated"
    dfOut2$ColorGroup[dfOut2$COG == "tp"] <- "tp"
  }
}

ggplot(dfOut2)+
  geom_bar(aes(x = factor(COG,levels = c("tp","na",COG_categories[!(COG_categories %in% c("na","tp"))])),
               y = Sig.rat*100,
               fill = ColorGroup),
             position = "stack",stat = "identity")+
  scale_fill_manual(values = c("unannotated" = "grey",
                               "Higher" = "red",
                               "Lower" = "blue",
                               "tp" = "black"),
                    labels = c("unannotated" = "Un-annotated",
                               "Higher" = "Higher",
                               "Lower" = "Lower",
                               "tp" = "Average"))+
  facet_wrap(facets = "phase.peaks", nrow = 4,ncol = 3)+
  labs(x = "COG category",
       y = "% significant contigs",
       fill = "Category")+
  theme_classic()

if(save_plots){
  ggsave("Chapter1_plots/COG_RainSigBars.png",dpi = 300,height = plot.height*4/3,width = plot.width*4/3)
}
  
```

```{r}
# view(Full.merged[Full.merged$Class == "Unresolved_Haptophyta",])
# 
# view(Full.merged[Full.merged$Division == "Haptophyta",])
# 
# 
# for(i in 1:length(top.Div)){
#   if(i == 1){
#     vec <- rep(NA,length(top.Div))
#   }
#   
#   vec[i] <- unique(Full.merged$Domain[Full.merged$Division %in% top.Div[i]])
# }


dfOut$Facet_Combo <- factor(paste(dfOut$Day.num, dfOut$ToD, sep = "_"),
                            levels = c("Day1_afternoon", "Day1_evening", "Day1_night", "Day1_morning",
                                       "Day2_night", "Day2_morning", "Day2_afternoon", "Day2_evening"))

ggplot(dfOut) +
    geom_bar(aes(fill = factor(Class, levels = c(top.Div, "other")),
                 x = Replicate,
                 y = TPM),
             position = "stack", stat = "identity") +
    facet_nested(~factor(Day.num, levels = c("Day1", "Day2"), labels = c("Day 1", "Day 2")) + Facet_Combo, 
                 scales = "free_x", space = "free_x") +
    theme_classic() +
    labs(x = "Sample",
         y = "Fraction of annotated TPM",
         title = "Top Species represented",
         fill = "Species") +
    scale_fill_manual(values = div.colors)+
    theme(axis.text.x = element_blank())

```

