---
title: "Eukaryote_subsection"
author: "Andreas Norlin"
date: "2023-10-13"
output: html_document
---

The initial code chunk (setup) is designed to clear the global environment, load the libraries needed for the code to run and to then load all the neccesary .csv.

Two meta data tables are loaded and merged together to get the HM (sample number) and the date and time for each sample. This data is also merged with the par data.

After the meta data is loaded, the subsectioned dataset is loaded and the temporal resolution of the par data is decreased to get a smaller sized data set for running the code quicker.

```{r setup, include=T}
knitr::opts_chunk$set(echo = TRUE)

#rm(list = ls())

package.list <- c("dplyr","tidyverse","ggplot2","lemon","vegan","Rmisc","lubridate")

if(!all(package.list %in% installed.packages()[,"Package"])){
  install.packages(package.list[!(package.list %in% installed.packages()[,"Package"])])
}

library(dplyr)
library(tidyverse)
library(ggplot2)
library(lemon)
library(vegan)
library(Rmisc)
library(lubridate)

#Loading the meta.data: meta.data1 is the Assmebly group and the sequencing ID (sample ID),
#meta.data2 is the data about sampling time and site.

meta.data1 <- read.csv("CSV_files/dielRNA_eukrythmic.tsv", sep = "\t")
meta.data2 <- read.csv("sample_metadata.csv") %>% 
  mutate(Sample_ID = paste("HM",Sample_ID,sep = ""))

names(meta.data2)[names(meta.data2) == "Sample_ID"] <- "SampleID"

#Combining meta.data1 and meta.data2 and making the lubri string a data + time saved in datetime
meta.data <- merge(meta.data1,meta.data2,by = "SampleID") %>% 
  mutate(datetime = ymd(substring(lubri,1,10))+hms(substring(lubri,12,19)))

meta.data <- separate(meta.data, col = AssemblyGroup, into = c("Day.num","ToD"),sep = "_",remove = FALSE, fill = "right", extra = "drop")

# meta.data$lubri <- with_tz(mdy_hms(meta.data$datetime, tz = "UTC"),
#                            tz = "America/Santiago")

COG_categories <- read.csv("CSV_files/COG_categories.csv",sep = ";")

Eukaryota.merged <- read.csv("CSV_files/Eukaryota.merged.csv")

par1 <- read.delim("NBP2113pguv.d342",  sep = " ", header =FALSE)
par2<- read.delim("NBP2113pguv.d343",  sep = " ", header =FALSE)
par3<- read.delim("NBP2113pguv.d344",  sep = " ", header =FALSE)

par = rbind(par1, par2, par3)[-1,c(1,2,3,10)]
names(par) <- c("juliendatetime","date", "time", "par")

partime <- par %>% 
  separate(juliendatetime, c("yearday","hour", "min", "sec"), sep = ":" ) %>% 
  unite(utctime, hour, min, sec, sep=":")  %>% 
  mutate(utcdatetime = paste(date, utctime))

partime$lubri <- with_tz(mdy_hms(partime$utcdatetime, tz = "UTC"),
                         tz = "America/Santiago")

for(i in 1:nrow(meta.data)){

  filter.above <- partime$lubri >= meta.data$datetime[i]
  filter.below <- partime$lubri < meta.data$datetime[i]
  
  vec.above <- partime[partime$lubri == min(partime$lubri[filter.above]),]
  vec.below <- partime[partime$lubri == max(partime$lubri[filter.below]),]
  
  meta.data$par[i] <- mean(vec.above$par,vec.below$par)
  
}

m <- 1
time.int <- ms("05.00")
for(i in 1:nrow(partime)){
  if(i == 1){
    vec <- NA
    vec.slide <- NA
    n <- 1
  }
  
  test.vec <- partime$lubri[i] - partime$lubri[m]
  
  if(test.vec > time.int){
    m <- i
    
    vec[n] <- i
    
    n <- n+1
  }
  
}

partime <- partime[vec,]
```

```{r}
df.merged <- Eukaryota.merged

filter <- nchar(df.merged$COG_category) == 1
df.merged_1COG <- df.merged[filter,] %>% 
  mutate(COG.untangled = df.merged$COG_category[filter],
         COG_level = "COG1")

df.merged_nCOG <- df.merged[!filter,] %>% 
  mutate(COG.untangled = NA)

for(i in 2:max(nchar(df.merged_nCOG$COG_category))){
  filter <- nchar(df.merged_nCOG$COG_category) == i
  
  df.temp <- df.merged_nCOG[filter,]
  
  for(j in 1:i){
    for(k in 1:nrow(df.temp)){
      df.temp$COG.untangled[k] <- substring(df.temp$COG_category[k],j,j)
    }
    
    df.temp <- df.temp %>% 
      mutate(COG_level = paste("COG",j,sep = ""))
    
    if(i == 2 & j == 1){
      df.untangled <- df.temp
    }else{
      df.untangled <- rbind(df.untangled,df.temp)
    }
  }
  
  if(i == max(nchar(df.merged_nCOG$COG_category))){
    df.merged <- rbind(df.merged_1COG,df.untangled)
  }
}

COG.vec <- unique(df.merged$COG.untangled)
n <- length(COG.vec)

day.vec <- paste(meta.data$SampleID,"_quant",sep = "")
m <- length(day.vec)

for(i in 1:n){ #Looping through the Classes to count the occurrences.
  
  COG.filter <- df.merged$COG.untangled == COG.vec[i]
  df.temp <- df.merged[COG.filter,]
  
  for(j in 1:m){ #Looping through the sampling time points.
    
   if(i == 1 & j == 1){ #Sets up an empty data.frame to input the data
     
     df.count <- data.frame(matrix(ncol = m, nrow = n))
     names(df.count) <- meta.data$SampleName
     
     df.count <- cbind(df.count,COG.vec)
   }
    
    df.count[i,j] <- sum(df.temp[,day.vec[j]])
    
  }
}

df.merged2 <- df.merged[df.merged$COG.untangled != "-",]

top5.vec <- names(table(df.merged2$COG.untangled)[order(-table(df.merged2$COG.untangled))[1:24]])

top5.filter <- df.count$COG.vec %in% c(top5.vec)

df.top5 <- df.count[top5.filter,]
df.other <- df.count[!top5.filter,]

df.count2 <- rbind(df.top5,c(colSums(df.other[,1:24]),"Other"))

order.vec <- c("morning",
               "afternoon",
               "evening",
               "night")

name_vec <- COG_categories$Description

names(name_vec) <- COG_categories$Category

dfOut <- pivot_longer(df.count2,
                      all_of(meta.data$SampleName),
                      names_to = "Day",
                      values_to = "Count") %>% 
  mutate(Count = as.numeric(Count))

dfOut$Day <- substring(dfOut$Day,1,nchar(dfOut$Day)-1)

df.summ <- summarySE(data = dfOut, "Count",
                     groupvars = c("Day","COG.vec"))

Day.Time <- meta.data[,c("AssemblyGroup","datetime","par","Day.num","ToD")] %>% 
  distinct(AssemblyGroup, .keep_all = TRUE)

names(Day.Time)[names(Day.Time) == "AssemblyGroup"] <- "Day"

dfOut2 <- merge(df.summ,Day.Time,by = "Day") #%>% mutate(COG.vec = factor(COG.vec, labels = name_vec))

p7 <- ggplot(dfOut2)+
  scale_y_continuous(sec.axis = sec_axis(~ ., name = "Secondary Y-axis"))+
  scale_fill_gradient(low = "black",high = "yellow")+
  # geom_line(aes(y = Count,
  #               x = factor(ToD, level = order.vec),
  #               color = Day.num))+
  geom_point(aes(y = Count,
                 x = factor(ToD, level = order.vec),
                 color = Day.num))+
  geom_errorbar(aes(y = Count,
                    x = factor(ToD, level = order.vec),
                    ymin = Count+sd,
                    ymax = Count-sd))+
  facet_wrap(facets = "COG.vec",
             nrow = 5,
             ncol = 5,
             scales = "free_y",
             labeller = function(variable,value){return(name_vec[value])})+
  labs(title = "TPM of each COG category for full data-set",
       y = expression(paste("TPM",sep = "",)),
       x = expression("Time of Day"))+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90,
                                   vjust = 0.5,
                                   hjust=1),
        legend.position = "right",
        axis.line.y.right = element_blank(),
        axis.title.y.right = element_blank(),
        axis.text.y.right = element_blank(),
        axis.ticks.y.right = element_blank(),
        strip.text.x = element_text(size = 6))+
  guides(fill = guide_legend(title = "COG"))

p7

ggsave("COG_Class_plots/COG_v_light_plot2.png",width = 15,height = 9,dpi = 300)
```

Initial exploration of the KEGG data, I found that there are so many different KEGGS if I use the first category in the string of the KEGG's after separating them.

```{r}
df.merged <- Eukaryota.merged

split_function <- function(x){
  strsplit(x,split = ",",fixed = TRUE)
}

for(i in 1:nrow(df.merged)){
  if(i == 1){
    n_KEGG <- length(unlist(split_function(df.merged$KEGG_ko[i])))
    n_GOs <- length(unlist(split_function(df.merged$GOs[i])))
    n_PFAMs <- length(unlist(split_function(df.merged$PFAMs[i])))
  }
  m_KEGG <- length(unlist(split_function(df.merged$KEGG_ko[i])))
  m_GOs <- length(unlist(split_function(df.merged$GOs[i])))
  m_PFAMs <- length(unlist(split_function(df.merged$PFAMs[i])))
  
  if(m_KEGG > n_KEGG){
    n_KEGG <- m_KEGG
  }
  
  if(m_GOs > n_GOs){
    n_GOs <- m_GOs
  }
  
  if(m_PFAMs > n_PFAMs){
    n_PFAMs <- m_PFAMs
  }
}

KEGG_columns <- paste("KEGG",1:n_KEGG,sep = "")

df.merged <- separate(df.merged,col = KEGG_ko,into = KEGG_columns,
                      sep = ",", remove = FALSE, fill = "right", extra = "drop")

PFAMs_columns <- paste("PFAMs",1:n_PFAMs,sep = "")

df.merged <- separate(df.merged,col = PFAMs,into = PFAMs_columns,
                      sep = ",", remove = FALSE, fill = "right", extra = "drop")

GOs_columns <- paste("GOs",1:n_GOs,sep = "")

df.merged <- separate(df.merged,col = GOs,into = GOs_columns,
                      sep = ",", remove = FALSE, fill = "right", extra = "drop")

n_KEGG
n_GOs
n_PFAMs

```


```{r}
df.merged <- Eukaryota.merged

filter <- df.merged$Class == "Prymnesiophyceae"

df.merged <- df.merged[filter,]

Species.vec <- unique(df.merged$Species)
n <- length(Species.vec)

day.vec <- paste(meta.data$SampleID,"_quant",sep = "")
m <- length(day.vec)

for(i in 1:n){ #Looping through the Classes to count the occurrences.
  
  Species.filter <- df.merged$Species == Species.vec[i]
  df.temp <- df.merged[Species.filter,]
  
  for(j in 1:m){ #Looping through the sampling time points.
    
   if(i == 1 & j == 1){ #Sets up an empty data.frame to input the data
     
     df.count <- data.frame(matrix(ncol = m, nrow = n))
     names(df.count) <- meta.data$SampleName
     
     df.count <- cbind(df.count,Species.vec)
   }
    
    df.count[i,j] <- sum(df.temp[,day.vec[j]])/sum(df.merged[,day.vec[j]])
    # df.count[i,j] <- sum(df.temp[,day.vec[j]])
    
  }
}
```

